---
title: "R Notebook"
output: html_notebook
---

```{r}
library(xlsx)
library(ggplot2)
```


```{r}
housing <- read.xlsx("data_g5.xlsx", sheetName = "6.19 r")
```

```{r}
head(housing)
```

1. Plot the series and briefly comment on the characteristics you observe (stationarity, trend,
seasonality, ...).

```{r}
ggplot(data = housing, aes(x = Fecha, y = X..Viviendas))+
  geom_line(color = "#00AFBB", size = 1.5) +
  labs(x = "Time", y = "% Houses")

```


2. Obtain a plot of the decomposition of the series, using stl(). Use an additive decomposition
or a multiplicative one, depending on your data. Use the function forecast() to forecast
future values. Multiplicative decomposition is useful when the logarithmic transformation
makes a difference in the appearance of your series and shows more constant variance. Does
the remainder look like a white noise to you? White noise is just a group of independent,
identically distributed variables, with zero mean and constant variance. Answer to this
point just visually or plot the ACF and PACF of the remainder part.


```{r}
housing_ts <- ts(housing[,2], frequency=12, start=c(1990,1))
stl.housing <- stl(housing_ts, t.window=5, s.window="periodic", robust=TRUE)
plot(stl.housing)
```

